---
title: "Tutorial 10 In-Class Check - Version D"
format:
  html:
    embed-resources: true
---

## Instructions

Answer all five questions.

Select the best answer in each case.

### Question 1

What is the best interpretation of the word *funnel* in this tutorial?

A. A sequence of steps through which users move, with some continuing and others dropping out.

B. A pricing strategy used to segment customers.

C. A method for cleaning missing values from experimental data.

D. A type of chart used only for demographics.

### Question 2

Consider the code below:

```{r}
#| eval: false
demogs <- 
    demogs |>
    inner_join(treatment, join_by(client_id))
```

What does this join accomplish?

A. It removes all clients who were assigned to Control.

B. It adds treatment-assignment information to the demographic data using the common client identifier.

C. It summarises the demographic data into one row per treatment.

D. It automatically tests for balance across groups.

### Question 3

Suppose a student says: "If completion is higher in the Test group, the new design must be better in every respect."

What is the best response?

A. Correct, because completion is the only outcome that matters.

B. Correct, because random assignment rules out all possible trade-offs.

C. Incorrect, because a higher completion rate could still mask friction or effort elsewhere in the process.

D. Incorrect, because experiments cannot measure completion rates.

### Question 4

Which code is most appropriate for keeping only rows with non-missing treatment labels after joining web log data?

A.

```{r}
#| eval: false
drop_na(variation)
```

B.

```{r}
#| eval: false
geom_bar(variation)
```

C.

```{r}
#| eval: false
facet_wrap(~ variation)
```

D.

```{r}
#| eval: false
labs(variation)
```

### Question 5

Why is event-level data especially useful for analysing user behaviour in a sign-up process?

A. It ensures that every client appears exactly once.

B. It allows us to reconstruct the sequence of actions users take within the process.

C. It automatically estimates the causal effect of treatment.

D. It removes the need for treatment assignment data.

::: {.callout-tip collapse="true"}
## Solution Key

1. **A**
   A funnel is a behavioural sequence of steps, where users either continue or drop out as they move through the process.

2. **B**
   The join merges treatment information into the demographic dataset using `client_id` as the shared key.

3. **C**
   Completion is important, but it does not by itself reveal whether users faced more friction or effort inside the process.

4. **A**
   `drop_na(variation)` keeps only observations with a usable treatment label.

5. **B**
   Because each action is recorded separately, event-level data let us study progression, drop-off, and other within-process behaviour.
:::
