---
title: "Tutorial 10 In-Class Check - Version B"
format:
  html:
    embed-resources: true
---

## Instructions

Answer all five questions.

Select the best answer in each case.

### Question 1

Rather than run an experiment, the firm could have changed the sign-up flow for everyone and compared completion rates before and after the change.

What is the main problem with this approach?

A. Before-and-after comparisons always produce smaller effects than experiments.

B. They make it impossible to calculate completion rates.

C. Before-and-after comparisons cannot isolate the effect of the design change from other things that may also have changed over time.

D. They remove the need for random assignment.

### Question 2

Why does random assignment matter in this setting?

A. It ensures that treatment users are always more engaged than control users.

B. It guarantees that the treatment effect will be positive.

C. It removes all missing data from the sample.

D. It helps make the groups comparable on average before outcomes are measured.

### Question 3

Consider the code below:

```{r}
#| eval: false
demogs |> 
    distinct(variation)
```

What is this step mainly checking?

A. Whether `variation` contains the expected treatment labels and any missing values.

B. Whether the dataset contains duplicate `client_id` values.

C. Whether completion rates are higher in the Test group.

D. Whether `variation` is a numeric variable.

### Question 4

A student combines two web log files using:

```{r}
#| eval: false
weblog <- 
    weblogs_files |> 
    map_df(read_csv)
```

What does `map_df()` do here?

A. It plots each dataset separately.

B. It reads each file and combines the results into one data frame.

C. It removes all duplicate rows automatically.

D. It keeps only users in the Test group.

### Question 5

Why is it important to remove duplicate rows from the web log data before constructing outcomes?

A. Duplicate rows make `read_csv()` fail.

B. Duplicate rows guarantee that `inner_join()` returns an empty dataset.

C. Duplicate rows can overstate user activity and distort later measures such as completion.

D. Duplicate rows prevent `clean_names()` from working.

::: {.callout-tip collapse="true"}
## Solution Key

1. **C**
   A before-and-after comparison mixes the design change with any other time-varying factor, so it weakens causal interpretation.

2. **D**
   Random assignment aims to make treatment and control groups comparable on average before outcomes are observed.

3. **A**
   `distinct(variation)` checks what values appear in the treatment variable, including whether anything unexpected or missing is present.

4. **B**
   `map_df(read_csv)` applies `read_csv()` to each file and binds the outputs together into one dataset.

5. **C**
   Duplicate event rows can inflate counts and produce misleading outcome measures.
:::
