---
title: "Tutorial 10 In-Class Check - Version A"
format:
  html:
    embed-resources: true
---

## Instructions

Answer all five questions.

Select the best answer in each case.

### Question 1

The company is testing a new sign-up flow before rolling it out to all users.

What is the best reason for doing this?

A. It guarantees that every user will complete the funnel.

B. It makes the treatment and control groups identical.

C. It removes the need to measure outcomes after the change.

D. It reduces the risk of rolling out a worse design to everyone.

### Question 2

Which statement best explains what a funnel can reveal that an overall completion rate cannot?

A. Whether the experiment used random assignment.

B. Which users were assigned to treatment.

C. Where in the process users are dropping off.

D. The exact revenue generated by each user.

### Question 3

Consider the code below:

```{r}
#| eval: false
treatment <- 
    read_csv("data/ab_test_experiment_clients.txt") |> 
    clean_names()
```

What problem does `clean_names()` help solve?

A. It standardises variable names so later joins and code are easier to write correctly.

B. It removes duplicate rows from the dataset.

C. It converts missing values into zeros.

D. It automatically checks whether treatment assignment was random.

### Question 4

Suppose a student wants to combine the demographic data with the treatment-assignment data.

Which code is most appropriate?

A.

```{r}
#| eval: false
distinct(demogs, treatment)
```

B.

```{r}
#| eval: false
inner_join(demogs, treatment, join_by(client_id))
```

C.

```{r}
#| eval: false
summarise(demogs, treatment)
```

D.

```{r}
#| eval: false
facet_wrap(demogs, treatment)
```

### Question 5

Which statement best describes event-level web log data?

A. Each row represents a single user, with exactly one row per client.

B. Each row represents one treatment group.

C. Each row is already a final outcome measure.

D. Each row represents an action taken by a user at a point in time.

::: {.callout-tip collapse="true"}
## Solution Key

1. **D**
   Testing limits the risk of exposing all users to a poorer sign-up experience before the firm has evidence on outcomes.

2. **C**
   A funnel shows where users drop off within the process, not just how many finish overall.

3. **A**
   `clean_names()` standardises column names, which reduces errors in later joins and manipulation.

4. **B**
   `inner_join(..., join_by(client_id))` correctly combines the two datasets using the shared client identifier.

5. **D**
   Event-level data record user actions over time, so each client can appear in multiple rows.
:::
