<!-- question-type: inclass -->
### Exercise 3: Working with Web Log Data

Now that you’ve checked that users were randomly assigned to the Test and Control groups, it's time to examine what they actually did inside the experiment. 

In this step, you’ll work with **event-level data** — information about each time a user interacted with the sign-up process.

**(a)** Load and inspect the web log data. The data are split across two files.  Run the code below to combine them into one dataset.

```{r}
#| eval: false
weblogs_files <- 
    c('data/ab_test_web_data_pt_1.txt',
      'data/ab_test_web_data_pt_2.txt')

weblog <- 
    weblogs_files |> 
    map_df(read_csv)

glimpse(YOURCODE)
```

What problem does `map_df()` solve here, and why might the data be stored across multiple files?

**(b)** Explain the structure of the data. What kind of information does each row represent? How is this different from the demographic dataset used earlier?

**(c)** A common problem when working with event log data is duplicate rows, where the same information is recorded multiple times. 

Clean the data to remove duplicate rows by completing the code below:

```{r}
#| eval: false
weblog_clean <- 
    weblog |> 
    YOURCODE
```

What might happen if we failed to remove duplicates before computing outcomes?

**(d)** Merge the cleaned web log data with the dataset that contains information on which clients are assigned to each treatment. Drop any observations that are not assigned to either "Test" or "Control".

```{r}
#| eval: false
weblog_clean <- 
    weblog_clean |> 
    YOUR_CODE |> 
    YOUR_CODE
```

Why do we restrict the dataset to users with valid treatment assignments before analysing behaviour?

<!-- BEGIN PROFILE:r-teaching-guide -->
::: {.content-visible when-profile="r-teaching-guide"}

::: {.teaching-block}

::: {.teaching-block-header}
Teaching Note
:::

::: {.teaching-block-body}
🎯 **Learning Objective**  

Students should:  

- Understand the structure and purpose of event-level (web log) data.  
- Learn how to combine and clean multiple files representing behavioural events.  
- Understand why web log data must be linked to treatment assignment before comparing behaviour across groups.
- Connect data cleaning and merging choices to the credibility of experimental analysis.

✅ **Core Concepts to Highlight**

- **Event-level vs. user-level data:**  
  Each row represents an action in time, not a person. This introduces sequence, timing, and frequency — enabling behavioural analysis (e.g., funnel progression).

- **Combining multiple data sources:**  
  Large-scale behavioural data are often split into multiple files for storage or collection reasons.  
  Using `map_df()` generalizes to real-world pipelines where analysts need to stitch data together.

- **Duplicates and data integrity:**  
  Duplicate events inflate counts and distort metrics like completion rates or average steps.  
  Always verify and clean before aggregation.

- **Linking behaviour to treatment:**
  Event data alone does not tell us whether a user was in Control or Test.
  Joining web logs to treatment assignment allows later comparisons of behaviour across variations.
  Restricting to valid treatment assignments ensures that only usable experimental observations are analysed.

- **Data preparation as part of causal analysis:**
  These are not merely technical housekeeping steps.
  They are part of making sure that later comparisons are meaningful and credible.

💬 **Suggested In-Class Prompts**

- “Why might we prefer to analyse event-level data instead of only final outcomes?”  
- “What could happen if duplicate events weren’t removed?”  
- “What are the trade-offs between `inner_join()` and `left_join()` here?”  
- “If a large share of users disappears after joining, what would that tell you about data quality?”  
- “How does this step prepare us for measuring completion or other behaviour”

📌 **Common Misunderstandings**

- Treating event data as if each row were a unique user.  
- Assuming all duplicates are errors without understanding possible system-level causes.  
- Thinking join type doesn’t matter even though it changes which users are included in the analysis.  
- Forgetting to check for missing variation labels before computing treatment effects.
- Believing that cleaning steps are purely technical rather than part of ensuring valid inference.

:::

:::

:::
<!-- END PROFILE:r-teaching-guide -->

<!-- BEGIN PROFILE:r-solutions -->
::: {.content-visible when-profile="r-solutions" when-profile="r-teaching-guide"}

::: {.solution-block}

::: {.solution-block-header}
Solution
:::

::: {.solution-block-body}

**(a)** 

```{r}
weblogs_files <- 
    c('data/ab_test_web_data_pt_1.txt',
      'data/ab_test_web_data_pt_2.txt')

weblog <- 
    weblogs_files |> 
    map_df(read_csv)

glimpse(weblog)
```

`map_df()` applies `read_csv()` to each file in `weblogs_files` and then combines the results into one dataset.

This is useful because it saves us from reading and binding each file manually.

The data may be stored across multiple files because behavioural datasets are often large, collected in batches, or split for storage and processing reasons.

**(b)** 

Each row represents a single user (`client_id`) taking some action (`process_step`) at a particular point in time (`date_time`).

This differs from the demographic dataset because:

- the demographic data are user-level, with one row per client
- the web log data are event-level, with multiple rows per client possible

**(c)** 

```{r}
weblog_clean <- 
    weblog |> 
    distinct()

```

`distinct()` drops any exact duplicate rows — ensuring that the same event isn’t counted twice.

Removing duplicates prevents over-counting when later computing events per user or funnel completion rates.

**(d)**

```{r}
weblog_clean <- 
    weblog_clean |> 
    inner_join(treatment, join_by(client_id)) |> 
    drop_na(variation)

```

Joining these data sets allows us to compare behaviour across the Test and Control groups.

`drop_na(variation)` removes observations without a valid treatment label. We restrict the dataset to users with valid treatment assignments because:

- only those users belong to the experiment in a usable way
- observations without treatment status cannot be placed in Control or Test
- keeping them would weaken the credibility of later comparisons

:::

:::

:::
<!-- END PROFILE:r-solutions -->