<!-- question-type: prepare -->
### Exercise 2: Exploring the Experimental Data

It’s time to look at the data from the experiment.

You have two datasets:  
- `ab_test_demographics`: information about each client.  
- `ab_test_experiment_clients`: information on which clients were assigned to the **Control** or **Test** variation.

Our goal is to merge these datasets and check whether allocation to treatment and control groups is balanced across deomgraphic characteristics.

**(a)** Load the two datasets into R by completing the code below:

```{r}
#| eval: false
demogs <- YOURCODE 
treatment <- 
    YOURCODE |> 
    clean_names()
```

**(b)** Merge the treatment indicator variable into the `demogs` data by completing the code below. We recommend you use an `inner_join()` to do this.

```{r}
#| eval: false
demogs <- 
    demogs |>
    YOURCODE

```

**(c)** What are the unique values in `variation` column? If needed, drop any rows of data that you won't be able to use in the Treatment vs Control comparison.

```{r}
#| eval: false
# how values in variation?
demogs |> 
    YOURCODE

# Perform any required operations to remove rows
# from the data
demogs <-
    demogs |> 
    YOURCODE
```

**(d)** In a well-designed experiment, each variation should include comparable types of users. How does connect back to the idea of random assignment?

**(e)** Complete the code below to compare demographic compositions of users across treatments. Explain your findings.

```{r}
#| eval: false
demogs |> 
    select(-client_id) |> 
    st(group = 'YOUR_TREATMENT_INDICATOR')
```


**(f)** Why is checking balance between treatments the first thing we do before comparing performance?

<!-- BEGIN PROFILE:r-teaching-guide -->
::: {.content-visible when-profile="r-teaching-guide"}

::: {.teaching-block}

::: {.teaching-block-header}
Teaching Note
:::

::: {.teaching-block-body}

🎯 **Learning Objective**  
Students should:  

- Learn how to combine demographic and experimental‐assignment data to prepare for analysis.  
- Understand why checking group balance is essential for credible experimental inference.  
- Recognize how random assignment supports fair comparison between treatment and control groups.  
- Connect data‐cleaning steps (joins, missing values) to experimental design logic.

✅ **Core Concepts to Highlight**

- **Data integration:**  
  Experiments often require merging multiple datasets (user characteristics + treatment allocation).  
  Clean joins are critical for ensuring every observation has complete information.

- **Uniqueness of identifiers:**  
  Each client ID should appear only once per dataset; duplicates threaten the logic of random assignment.

- **Random assignment and balance:**  
  If assignment worked, demographic characteristics should be evenly distributed across variations.  
  Balance gives confidence that outcome differences later reflect the experimental change.

- **Interpreting balance tables:**  
  Nearly identical means or proportions across groups indicate success.  
  Minor random variation is expected; systematic gaps signal implementation issues.

- **Why balance matters first:**  
  Establishing comparability before outcome analysis preserves causal credibility.

💬 **Suggested In-Class Prompts**

- “What could happen if one group had systematically older or more experienced users?”
- “Why might a random process still produce small imbalances?”  
- “How would you explain to a manager why we check balance before looking at results?”
- [Advanced] "How could we test whether there are differences between treatments?"
- “If random assignment failed, can we still interpret completion differences as causal?”

📌 **Common Misunderstandings**

- Expecting perfect (identical) balance rather than approximate similarity.  
- Thinking balance checks are only about fairness rather than validity of inference.  


:::

:::

:::
<!-- END PROFILE:r-teaching-guide -->

<!-- BEGIN PROFILE:r-solutions -->
::: {.content-visible when-profile="r-solutions" when-profile="r-teaching-guide"}

::: {.solution-block}

::: {.solution-block-header}
Solution
:::

::: {.solution-block-body}

**(a)**  
Load both datasets and inspect them.

```{r}
demogs <- 
    read_csv("data/ab_test_demographics.txt")
treatment <- 
    read_csv("data/ab_test_experiment_clients.txt") |> 
    janitor::clean_names()
```

**(b)** 

```{r}
demogs <- 
    demogs |>
    inner_join(treatment, join_by(client_id))
```

**(c)**

```{r}
# view unique values
demogs |> 
    distinct(variation)

# drop missing or unusable rows
demogs <- 
    demogs |> 
    drop_na(variation)
```

**(d)** 
In a well-designed experiment, both variations should contain similar types of users.
This connects directly to the idea of random assignment — if users are randomly allocated, differences in demographics should appear only by chance.
Balanced characteristics increase confidence that later performance differences are due to the new sign-up flow, not underlying user differences.

**(e)** 
Compare demographic balance across treatments.

```{r}
demogs |> 
    select(-client_id) |> 
    st(group = 'variation')
```

The summary table (`st()`) should show nearly identical means and proportions across groups.

Small random differences are expected, but no systematic gaps should appear.

**(f)**
Checking balance is the first step before comparing performance because:

- It verifies that random assignment was implemented correctly.
- If groups differ systematically at baseline, outcome differences could reflect pre-existing characteristics rather than the experimental change.
- Confirming balance ensures that any observed effects can be credibly attributed to the new sign-up flow.
:::

:::

:::
<!-- END PROFILE:r-solutions -->