<!-- question-type: prepare -->
### Exercise 2: Exploring the Experimental Data

It’s time to look at the data from the experiment.

You have two datasets:  
- `ab_test_demographics`: information about each client.  
- `ab_test_experiment_clients`: information on which clients were assigned to the **Control** or **Test** variation.

Our goal is to merge these datasets and check whether allocation to treatment and control groups is balanced across demographic characteristics.

**(a)** Load the two datasets into R by completing the code below:

```{r}
#| eval: false
demogs <- YOUR_CODE 
treatment <- 
    YOUR_CODE |> 
    clean_names()
```

What problem does `clean_names()` solve, and how might inconsistent column names affect later steps?

**(b)** Merge the treatment indicator variable into the `demogs` data by completing the code below. We recommend you use an `inner_join()` to do this.

```{r}
#| eval: false
demogs <- 
    demogs |>
    YOUR_CODE

```

What does a join do in this context, and why must these datasets be combined before analysing the experiment?

**(c)** Next, we want to inspect and clean the treatment variable. First, use `distinct()` to find the values that `variation` takes in our dataset.

```{r}
#| eval: false
demogs |> 
    YOUR_CODE
```

What is this step checking, and why is it important to verify these values before proceeding?

Second, use `drop_na()` to remove rows with missing treatment labels.

```{r}
#| eval: false
demogs <-
    demogs |> 
    YOUR_CODE
```

Why do we drop these observations?

**(d)** In a well-designed experiment, each variation should include comparable types of users. How does this connect back to the idea of random assignment?

**(e)** Complete the code below to compare demographic compositions of users across treatments.

```{r}
#| eval: false
demogs |> 
    select(-client_id) |> 
    st(group = 'YOUR_TREATMENT_INDICATOR')
```

What is this table helping us assess, and why do we check this before comparing outcomes?

<!-- BEGIN PROFILE:r-teaching-guide -->
::: {.content-visible when-profile="r-teaching-guide"}

::: {.teaching-block}

::: {.teaching-block-header}
Teaching Note
:::

::: {.teaching-block-body}

🎯 **Learning Objective**  
Students should:  

- Learn how to combine demographic and experimental‐assignment data to prepare for analysis.  
- Understand why checking group balance is essential for credible experimental inference.  
- Recognise how random assignment supports fair comparison between treatment and control groups.  
- Connect data‐cleaning steps (joins, missing values) to experimental design logic.

✅ **Core Concepts to Highlight**

- **Data integration:**  
  - Experiments often require merging multiple datasets (user characteristics + treatment allocation).  
  - Clean joins are critical for ensuring every observation has complete information.

- **Uniqueness of identifiers:**  
  - Each client ID should appear only once per dataset; duplicates threaten the logic of random assignment.

- **Random assignment and balance:**  
  - If assignment worked, demographic characteristics should be evenly distributed across variations.  
  - Balance gives confidence that outcome differences later reflect the experimental change.

- **Interpreting balance tables:**  
  - Nearly identical means or proportions across groups indicate success.  
  - Minor random variation is expected; systematic gaps signal implementation issues.

- **Why balance matters first:**  
  - Establishing comparability before outcome analysis preserves causal credibility.

💬 **Suggested In-Class Prompts**

- “What could happen if one group had systematically older or more experienced users?”
- “Why might a random process still produce small imbalances?”  
- “How would you explain to a manager why we check balance before looking at results?”
- [Advanced] "How could we test whether there are differences between treatments?"
- “If random assignment failed, can we still interpret completion differences as causal?”

📌 **Common Misunderstandings**

- Treating data cleaning as a purely technical step rather than part of inference.
- Assuming joins are mechanical rather than conceptually important.
- Expecting perfect (identical) balance rather than approximate similarity.  
- Thinking balance checks are only about fairness rather than validity of inference.  


:::

:::

:::
<!-- END PROFILE:r-teaching-guide -->

<!-- BEGIN PROFILE:r-solutions -->
::: {.content-visible when-profile="r-solutions" when-profile="r-teaching-guide"}

::: {.solution-block}

::: {.solution-block-header}
Solution
:::

::: {.solution-block-body}

**(a)**  

```{r}
demogs <- 
    read_csv("data/ab_test_demographics.txt")
treatment <- 
    read_csv("data/ab_test_experiment_clients.txt") |> 
    janitor::clean_names()
```

`clean_names()` standardises column names into a consistent format, usually lowercase with underscores. This is useful because consistent variable names reduce errors and make later joins and data manipulation easier.

**(b)** 

```{r}
demogs <- 
    demogs |>
    inner_join(treatment, join_by(client_id))
```

A join combines the demographic data with the treatment assignment data using the common identifier `client_id`.

This is necessary because:

-  The demographic dataset contains user characteristics
-  The treatment dataset contains variation assignment

We need both in the same dataset before we can compare treatment groups (and so assess balance).

**(c)**

```{r}
# view unique values
demogs |> 
    distinct(variation)
```

This checks the unique values in the variation variable. 
It is important because we need to verify that the treatment variable contains usable categories such as "Control" and "Test", and identify missing or unexpected values.

```{r}
# drop missing or unusable rows
demogs <- 
    demogs |> 
    drop_na(variation)
```

This removes rows where variation is missing.
We do this because observations without a valid treatment assignment cannot be used in a treatment-versus-control comparison.

**(d)** 
In a well-designed experiment, both variations should contain similar types of users.
This connects directly to the idea of random assignment — if users are randomly allocated, differences in demographics should appear only by chance.
Balanced characteristics increase confidence that later performance differences are due to the new sign-up flow, not underlying user differences.

**(e)** 

```{r}
demogs |> 
    select(-client_id) |> 
    st(group = 'variation')
```

We check balance first because it verifies that the experimental design was implemented credibly.
The summary table (`st()`) should show nearly identical means and proportions across groups. Small random differences are expected, but no systematic gaps should appear.

If Control and Test differ systematically at baseline, then later differences in completion or behaviour may not be caused by the new sign-up flow. And so, checking balance first protects the credibility of the causal comparison.



:::

:::

:::
<!-- END PROFILE:r-solutions -->
