<!-- question-type: inclass -->
### Exercise 4: Measuring Funnel Completion

Now that we've linked event-level data with the experimental information, let's create our first outcome measure: **funnel completion**.

Each client goes through a series of process steps (for example, `start`, `step_1`, `step_2`, `confirm`).  
A funnel *completion* occurs if the client reaches the final step, `"confirm"`.

**(a)** Compute a client-level indicator for whether each client completed the funnel by completing the code below.

```{r}
#| eval: false
completion_by_visitor <- 
    YOUR_CODE |>
    group_by(YOUR_CODE) |>
    YOUR_CODE(
        completed = any(YOUR_CODE == "confirm"),
        .groups = "drop"
    )

```

What does `any()` do here, and why must we aggregate from event-level data to client-level outcomes?

**(b)** We want see if the new sign-up process 'works'. And so, we first need to summarise completion rates by treatment.

```{r}
#| eval: false
completion_summary <- 
    YOUR_CODE |>
    YOUR_CODE |>
    summarise(
        completes = YOUR_CODE,
        total     = YOUR_CODE,
        pct       = completes / total * 100,
        .groups   = "drop"
    )

```

What do `completes`, `total`, and `pct` represent, and why do we summarize at the treatment-group level?

**(c)** Create a simple visual to compare completion rates across the two variations. Use a bar chart to display the percentage of users who completed the funnel.

```{r}
#| eval: false
completion_summary |> 
    YOUR_CODE +
    YOUR_CODE +
    geom_text(aes(label = round(pct, 1)), vjust = -0.5) +
    labs(
        title = "Funnel Completion Rate by Variation",
        x = "Variation",
        y = "Completion Rate (%)"
    ) +
    theme_minimal() +
    theme(legend.position = "none")
```

What does this visual add beyond the table, and why is a simple chart often preferred in a business setting?

**(d)** Interpret your findings. By how many percentage points did the change in sign up process influence completions?

<!-- BEGIN PROFILE:r-teaching-guide -->
::: {.content-visible when-profile="r-teaching-guide"}

::: {.teaching-block}

::: {.teaching-block-header}
Teaching Note
:::

::: {.teaching-block-body}

🎯 **Learning Objective**  
Students should:  

- Understand how to construct a user-level outcome from event-level data.
- Interpret how completion rates are calculated and compared across treatment groups.
- Recognise how results should be communicated to a business audience.
- Distinguish between percentage points and percent change when interpreting results.

✅ **Core Concepts to Highlight**

- **Aggregation and granularity:**  
  Explain how summarising event-level actions to the client level captures whether each user “succeeded” in completing the funnel.

- **Outcome definition:**  
  The choice of “completion” as the outcome connects directly to the business question: *Did the new sign-up flow help more users finish?*

- **Descriptive comparison:**  
  Computing and plotting completion rates is the first step toward evaluating impact — but these are still *descriptive statistics*, not causal claims.

- **Percentage vs. percentage points:**  
  A difference between 65.6 % and 69.3 % is **3.7 percentage points**, not “3.7 % improvement.”  
  Reinforce this distinction — it’s critical for clean business communication.

- **Visualization for stakeholders:**  
  A simple bar chart makes the result accessible to non-technical audiences and aligns with how analytics teams typically communicate A/B test results.

💬 **Suggested In-Class Prompts**

- “Why do we calculate this at the *client* level instead of the *event* level?”  
- “If we see a 3.7 percentage-point difference, is that large or small in this context?”  
- “How might we explain this result to a product manager in one sentence?”  
- “What are some reasons the Test group might outperform the Control beyond the design change itself?”  

📌 **Common Misunderstandings**

- Confusing *percentage points* (absolute difference) with *percent change* (relative difference).  
- Forgetting that descriptive differences alone don’t confirm causality.  
- Assuming visualizations replace numerical summaries rather than complement them.  
- Interpreting the `any()` function incorrectly (thinking it counts events instead of checking existence).  
- Ignoring potential data issues such as missing or duplicated user IDs when summarising.


:::

:::

:::
<!-- END PROFILE:r-teaching-guide -->

<!-- BEGIN PROFILE:r-solutions -->
::: {.content-visible when-profile="r-solutions" when-profile="r-teaching-guide"}

::: {.solution-block}

::: {.solution-block-header}
Solution
:::

::: {.solution-block-body}

**(a)** 

```{r}
completion_by_visitor <- 
    weblog_clean |>
    group_by(variation, client_id) |>
    summarise(
        completed = any(process_step == "confirm"),
        .groups = "drop"
    )
```

The `any(process_step == "confirm")` condition checks whether a client ever reached the "confirm" step.

This converts multiple event-level rows into a single user-level outcome:

- TRUE if the user completed the funnel
- FALSE otherwise

We aggregate because the data are recorded at the event level, but the outcome of interest is defined at the user level.

**(b)**

```{r}
completion_summary <- 
    completion_by_visitor |>
    group_by(variation) |>
    summarise(
        completes = sum(completed),
        total     = n(),
        pct       = completes / total * 100,
        .groups   = "drop"
    )
```

This summary table provides the key comparison for the experiment.

We have the following arguments inside `summarise()`:
- `completes` = number of users who completed
- `total` = number of users in each group
- `pct` = percentage of users who completed

We summarise at the treatment-group level to compare outcomes between Control and Test.

**(c)** 
```{r}
completion_summary |> 
    ggplot(aes(x = variation, y = pct, fill = variation)) +
    geom_col() +
    geom_text(aes(label = round(pct, 1)), vjust = -0.5) +
    labs(
        title = "Funnel Completion Rate by Variation",
        x = "Variation",
        y = "Completion Rate (%)"
    ) +
    theme_minimal() +
    theme(legend.position = "none")
```

The plot visually compares completion rates across variations.

Bars make it easy to see which variation performs better and by how much.

Adding text labels helps decision-makers read exact percentages directly from the chart.

**(d) ** Interpretation

The difference in completion rates (in percentage points) represents the estimated effect of the new sign-up flow.

Control = 65.6 and Test = 69.3%, then the Test version increased completions by 3.7 percentage points.

We report percentage points because:

- they measure absolute differences in rates
- they are clearer and standard in business settings

Because treatment was randomly assigned and balance was confirmed earlier, this difference can be interpreted as the causal effect of the new design.

:::

:::

:::
<!-- END PROFILE:r-solutions -->