<!-- question-type: inclass -->
### Exercise 4: Measuring Funnel Completion

Now that we've linked event-level data with the experimental information, let's create our first outcome measure: **funnel completion**.

Each client goes through a series of process steps (for example, `start`, `step_1`, `step_2`, `confirm`).  
A funnel *completion* occurs if the client reaches the final step, `"confirm"`.

**(a)** Compute a client-level indicator for whether each client completed the funnel by completing the code below.

```{r}
#| eval: false
completion_by_visitor <- 
    YOUR_CODE |>
    group_by(YOUR_CODE) |>
    YOUR_CODE(
        completed = any(YOUR_CODE == "confirm"),
        .groups = "drop"
    )

```

What does `any()` do here, and why must we aggregate from event-level data to client-level outcomes?

**(b)** We want to see if the new sign-up process is more effective. Therefore, we first need to summarise completion rates by treatment.

```{r}
#| eval: false
completion_summary <- 
    YOUR_CODE |>
    YOUR_CODE |>
    summarise(
        completes = YOUR_CODE,
        total     = YOUR_CODE,
        pct       = completes / total * 100,
        .groups   = "drop"
    )

```

What do `completes`, `total`, and `pct` represent, and why do we summarize at the treatment-group level?

**(c)** Create a simple visual to compare completion rates across the two variations. Use a bar chart to display the percentage of users who completed the funnel.

```{r}
#| eval: false
completion_summary |> 
    YOUR_CODE +
    YOUR_CODE +
    geom_text(aes(label = round(pct, 1)), vjust = -0.5) +
    labs(
        title = "Funnel Completion Rate by Variation",
        x = "Variation",
        y = "Completion Rate (%)"
    ) +
    theme_minimal() +
    theme(legend.position = "none")
```

What does this visual add beyond the table, and why is a simple chart often preferred in a business setting?

**(d)** Complete the code below to compute and interpret the 'effect' of the new sign-up process on completion. Use `lag()` to compare the Test group to the previous row after ordering the summary table.

```{r}
#| eval: false
completion_diff <- 
    completion_summary |> 
    arrange(YOUR_CODE) |> 
    mutate(diff_pct_points = YOUR_CODE) |> 
    summarise(diff_pct_points = YOUR_CODE)

completion_summary |> 
    arrange(YOUR_CODE) |> 
    mutate(
        pct_change = YOUR_CODE
    )
```

Because the Control row has no previous row, the `lag()` result for Control will be missing. Report the Test row's difference.

By how many percentage points did the change in sign-up process influence completions? What is the difference in percentage points and percent change, and why do we typically report percentage points in this setting?

**(e)** Complete the code below to express the effect size in standard deviation units.

```{r}
#| eval: false
diff_rate <- completion_diff |> 
    pull(diff_pct_points) / 100

control_sd <- 
    completion_by_visitor |> 
    YOUR_CODE |> 
    YOUR_CODE(sd_rate = YOUR_CODE) |> 
    pull(sd_rate)

diff_sd_units <- diff_rate / control_sd
print(diff_sd_units)
```

What does dividing by the standard deviation tell us about the size of the effect? What does this help us better understand?

**(f)** Would you consider this a small, moderate, or large effect in a typical online experiment? Explain your answer.


<!-- BEGIN PROFILE:r-teaching-guide -->
::: {.content-visible when-profile="r-teaching-guide"}

::: {.teaching-block}

::: {.teaching-block-header}
Teaching Note
:::

::: {.teaching-block-body}

🎯 **Learning Objective**  
Students should:  

- Construct a user-level outcome from event-level data.
- Compute and compare completion rates across treatment groups.
- Distinguish between percentage points and percent change.
- Interpret effect size in both statistical and economic terms.
- Evaluate whether an effect is meaningful in a business context.

✅ **Core Concepts to Highlight**

- **Event → outcome:**
  - Web log data record actions, not outcomes.
  - Aggregation is required to define whether a user completed the funnel.
  - `any()` detects whether completion occurred at least once.

- **Measurement and communication:**
  - Completion rates summarise performance across users.
  - Group-level summaries enable comparison between Control and Test.
  - Simple visuals communicate differences more clearly than tables.

- **Units of comparison:**
  - Percentage points measure absolute differences in rates.
  - Percent change measures relative improvement.
  - In product and business settings, percentage points are the default.
  - If students use `lag()`, they must order the rows first so the comparison is meaningful.

- **Effect size (statistical interpretation):**
  - Dividing by the standard deviation expresses the effect in SD units.
  - This provides a scale-free measure of magnitude.
  - Typical online experiments produce small effects (≈ 0.02–0.10 SD).

- **Economic significance (business interpretation):**
  - Small statistical effects can still be valuable at scale.
  - A back-of-the-envelope calculation connects to percentage-point changes to economic value.

💬 **Suggested In-Class Prompts**

- “Why do we report percentage points rather than percent change?”
- “Does a 3–4 p.p. lift matter if the platform has millions of users?”
- “What does 0.08 SD mean in practical terms?”
- “Why are small effects common in real-world experiments?”
- “How would you explain this result to a product manager in one sentence?”

📌 **Common Misunderstandings**

- Confusing percentage points with percent change.
- Interpreting small SD effects as unimportant.
- Focusing only on statistical magnitude rather than economic impact.
- Forgetting that causal interpretation depends on earlier steps (randomisation and balance).

:::

:::

:::
<!-- END PROFILE:r-teaching-guide -->

<!-- BEGIN PROFILE:r-solutions -->
::: {.content-visible when-profile="r-solutions" when-profile="r-teaching-guide"}

::: {.solution-block}

::: {.solution-block-header}
Solution
:::

::: {.solution-block-body}

**(a)** 

```{r}
completion_by_visitor <- 
    weblog_clean |>
    group_by(variation, client_id) |>
    summarise(
        completed = any(process_step == "confirm"),
        .groups = "drop"
    )
```

The `any(process_step == "confirm")` condition checks whether a client ever reached the "confirm" step.

This converts multiple event-level rows into a single user-level outcome:

- TRUE if the user completed the funnel
- FALSE otherwise

We aggregate because the data are recorded at the event level, but the outcome of interest is defined at the user level.

**(b)**

```{r}
completion_summary <- 
    completion_by_visitor |>
    group_by(variation) |>
    summarise(
        completes = sum(completed),
        total     = n(),
        pct       = completes / total * 100,
        .groups   = "drop"
    )
```

This summary table provides the key comparison for the experiment.

We have the following arguments inside `summarise()`:

- `completes` = number of users who completed
- `total` = number of users in each group
- `pct` = percentage of users who completed

We summarise at the treatment-group level to compare outcomes between Control and Test.

**(c)** 
```{r}
completion_summary |> 
    ggplot(aes(x = variation, y = pct, fill = variation)) +
    geom_col() +
    geom_text(aes(label = round(pct, 1)), vjust = -0.5) +
    labs(
        title = "Funnel Completion Rate by Variation",
        x = "Variation",
        y = "Completion Rate (%)"
    ) +
    theme_minimal() +
    theme(legend.position = "none")
```

The plot visually compares completion rates across variations.

Bars make it easy to see which variation performs better and by how much.

Adding text labels helps decision-makers read exact percentages directly from the chart.

**(d)** 

```{r}
completion_diff <- 
    completion_summary |> 
    arrange(variation) |> 
    mutate(diff_pct_points = pct - lag(pct)) |> 
    summarise(diff_pct_points = last(diff_pct_points))

completion_summary |> 
    arrange(variation) |> 
    mutate(
        pct_change = (pct - lag(pct)) / lag(pct) * 100
    )
```

The difference in completion rates (in percentage points) represents the estimated effect of the new sign-up flow.

After ordering the rows so that Control comes before Test, `lag()` uses the Control completion rate as the comparison point for the Test row.

If Control = 65.6 and Test = 69.3%, then the Test version increased completions by 3.7 percentage points, or ~5.6%.

We report percentage points because:

- they measure absolute differences in rates
- they are clearer and standard in business settings

Because treatment was randomly assigned and balance was confirmed earlier, this difference can be interpreted as the causal effect of the new design.

**(e)** 

```{r}
diff_rate <- completion_diff |>
    pull(diff_pct_points) / 100

control_sd <- 
    completion_by_visitor |> 
    filter(variation == "Control") |> 
    summarise(sd_rate = sd(completed)) |> 
    pull(sd_rate)

diff_sd_units <- diff_rate / control_sd
print(diff_sd_units)
```

This expresses the treatment effect in standard deviation units.

- `control_sd` measures the natural variation in completion outcomes.
- Dividing the effect by the SD shows how large the effect is relative to that variation.

An effect of around 0.08 SD is small in statistical terms but typical for online experiments.

This provides a scale-free measure of magnitude, helping us judge whether the effect is meaningful beyond just the raw percentage-point difference.

**(f)**

The effect is small in statistical terms (~0.08 SD), but can still be economically meaningful.

For example:

- If 1,000,000 users go through the process, a 3.7 p.p. increase yields ≈ 37,000 additional completions.

If each completion is worth:

- $10 → ≈ $370,000
- $50 → ≈ $1.85 million

Even modest improvements in conversion can therefore generate large gains at scale.

:::

:::

:::
<!-- END PROFILE:r-solutions -->
