<!-- question-type: inclass -->
### Exercise 4: Measuring Funnel Completion

Now that we've linked event-level data with the experimental information, let's create our first outcome measure — **funnel completion**.

Each client goes through a series of process steps (for example, `start`, `step_1`, `step_2`, `confirm`).  
A funnel *completion* occurs if the client reaches the final step, `"confirm"`.

**(a)** Compute a client-level indicator for whether each client completed the funnel by completing the code below.

```{r}
#| eval: false
completion_by_visitor <- 
    YOUR_CODE |>
    group_by(YOUR_CODE) |>
    YOUR_CODE(
        completed = any(YOUR_CODE == "confirm"),
        .groups = "drop"
    )

```

**(b)** Summarise completion rates by treatment.

```{r}
#| eval: false
completion_summary <- 
    YOUR_CODE |>
    YOUR_CODE |>
    summarise(
        completes = YOUR_CODE,
        total     = YOUR_CODE,
        pct       = completes / total * 100,
        .groups   = "drop"
    )

```

**(c)** Create a simple visual to compare completion rates across the two variations. Use a bar chart to display the percentage of users who completed the funnel.

```{r}
#| eval: false
completion_summary |> 
    YOUR_CODE +
    YOUR_CODE +
    geom_text(aes(label = round(pct, 1)), vjust = -0.5) +
    labs(
        title = "Funnel Completion Rate by Variation",
        x = "Variation",
        y = "Completion Rate (%)"
    ) +
    theme_minimal() +
    theme(legend.position = "none")
```

**(d)** Interpret your findings. By how many percentage points did the change in sign up process influence completions?

<!-- BEGIN PROFILE:r-teaching-guide -->
::: {.content-visible when-profile="r-teaching-guide"}

::: {.teaching-block}

::: {.teaching-block-header}
Teaching Note
:::

::: {.teaching-block-body}

🎯 **Learning Objective**  
Students should:  
- Learn how to summarise event-level data into client-level outcomes.  
- Understand how to calculate and interpret funnel completion rates across experimental groups.  
- Recognize the importance of clear visual and numerical comparisons when communicating results.  
- Begin linking descriptive differences to the logic of causal effects (without formal inference yet).

✅ **Core Concepts to Highlight**

- **Aggregation and granularity:**  
  Explain how summarising event-level actions to the client level captures whether each user “succeeded” in completing the funnel.

- **Outcome definition:**  
  The choice of “completion” as the outcome connects directly to the business question: *Did the new sign-up flow help more users finish?*

- **Descriptive comparison:**  
  Computing and plotting completion rates is the first step toward evaluating impact — but these are still *descriptive statistics*, not causal claims.

- **Percentage vs. percentage points:**  
  A difference between 65.6 % and 69.3 % is **3.7 percentage points**, not “3.7 % improvement.”  
  Reinforce this distinction — it’s critical for clean business communication.

- **Visualization for stakeholders:**  
  A simple bar chart makes the result accessible to non-technical audiences and aligns with how analytics teams typically communicate A/B test results.

💬 **Suggested In-Class Prompts**

- “Why do we calculate this at the *client* level instead of the *event* level?”  
- “If we see a 3.7 percentage-point difference, is that large or small in this context?”  
- “How might we explain this result to a product manager in one sentence?”  
- “What are some reasons the Test group might outperform the Control beyond the design change itself?”  

📌 **Common Misunderstandings**

- Confusing *percentage points* (absolute difference) with *percent change* (relative difference).  
- Forgetting that descriptive differences alone don’t confirm causality.  
- Assuming visualizations replace numerical summaries rather than complement them.  
- Interpreting the `any()` function incorrectly (thinking it counts events instead of checking existence).  
- Ignoring potential data issues such as missing or duplicated user IDs when summarising.


:::

:::

:::
<!-- END PROFILE:r-teaching-guide -->

<!-- BEGIN PROFILE:r-solutions -->
::: {.content-visible when-profile="r-solutions" when-profile="r-teaching-guide"}

::: {.solution-block}

::: {.solution-block-header}
Solution
:::

::: {.solution-block-body}

**(a)** Compute a client-level indicator for whether each client completed the funnel.

```{r}
completion_by_visitor <- 
    weblog_clean |>
    group_by(variation, client_id) |>
    summarise(
        completed = any(process_step == "confirm"),
        .groups = "drop"
    )
```

The `any(process_step == "confirm")` condition checks whether a client ever reached the "confirm" step.

The grouping ensures this is calculated per client and per variation. The latter simply keeps the treatment allocation attached to the summary data

The resulting dataset has one row per client, indicating whether they completed (TRUE) or not (FALSE).

**(b)** Summarise completion rates by treatment.

```{r}
completion_summary <- 
    completion_by_visitor |>
    group_by(variation) |>
    summarise(
        completes = sum(completed),
        total     = n(),
        pct       = completes / total * 100,
        .groups   = "drop"
    )
```

`sum(completed)` counts how many clients completed the funnel.

`n()` counts how many total clients were in that variation.

Dividing gives a percentage completion rate (pct) for each variation.

This summary table provides the key comparison for the experiment.

**(c)** 
```{r}
completion_summary |> 
    ggplot(aes(x = variation, y = pct, fill = variation)) +
    geom_col() +
    geom_text(aes(label = round(pct, 1)), vjust = -0.5) +
    labs(
        title = "Funnel Completion Rate by Variation",
        x = "Variation",
        y = "Completion Rate (%)"
    ) +
    theme_minimal() +
    theme(legend.position = "none")
```

The plot visually compares completion rates across variations.

Bars make it easy to see which variation performs better and by how much.

Adding text labels helps decision-makers read exact percentages directly from the chart.

**(d) ** Interpretation

The difference in completion rates (in percentage points) represents the estimated effect of the new sign-up flow.

Control = 65.6 and Test = 69.3%, then the Test version increased completions by 3.7 percentage points.
:::

:::

:::
<!-- END PROFILE:r-solutions -->